Reliable Inferences from Simply Parameterised Models

### 2012-08-29 ms.tex
The formula for the simulated data

\subsection{Complex Models}
The second category of models we consider are ``complex'' models. These tend to
be much more flexible and contain large numbers of unknown parameters. Complex
models are often incorrectly referred to as nonparametric models. A better term
would be flexible models or free-form models.

The primary advantage of complex models is realism. The universe is not
simple place, and it is rare that a physical situation can be described accurately
by a simply-parameterised model which is often a single mathematical equation.

\section{Example 1: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data in order to estimate the total flux of the line.

>>>>

\subsection{Complex Models}
The second category of models we consider are ``complex'' models. These tend to
be much more flexible and contain large numbers of unknown parameters. Complex
models are often incorrectly referred to as nonparametric models. A better term
would be flexible models or free-form models. The primary advantage of complex models is realism. The universe is not
simple place, and it is rare that a physical situation can be described accurately
by a simply-parameterised model which is often a simple mathematical formula.

\section{An Example: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data to explore the properties of simply parameterised models. The
simulated data was generated from the following complex model:
\begin{eqnarray}
\mathcal{M}_0(x) \propto 3\exp\left[-\frac{1}{2}\left(\frac{x}{0.3}\right)^2\right]
+ \exp\left[-\frac{1}{2}\left(\frac{x - 1}{1}\right)^2\right]
+ 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
\end{eqnarray}
The fluxes were evaluated at $x$-values ranging from $-10$ to $10$ in steps
of $0.001$, and then normalised to sum to 1:
\begin{eqnarray}
\sum_{i=1}^N \mathcal{M}_0(x_i) &=& 1.
\end{eqnarray}
